Generate data for NOBA cod ensemble modeling

### 2021-05-05 NOBAcod.Rmd
modify NOBAcod script to create SSmodel

require(r4ss)
omlist_ss<-CC3om_sardine
source(here("/config/CC3Config_sardLWcorr.R"))
source(here("/config/omdimensions.R"))
source(here("/config/sardinesurvey.R"))
source(here("/config/sardinefishery.R"))

#Directory with SS files
model_dir <- "Sardine_SS_files/"

#Name of SS data file
datfile_name <- "sardEM_3_3.dat"

@@

#Month of survey/fishing
survey_month <- 7
fishing_month <- 1

>>>>

require(r4ss)
#omlist_ss<- ?
source(here("config/omdimensions.R"))
source(here("/config/codsurvey.R"))
source(here("/config/codfishery.R"))

#Directory with SS files
model_dir <- "NOBA_cod_files/"

#Name of SS data file
datfile_name <- "ss3.dat"

@@

#Load in model object from SAM
noba_cod_out <- system.file("inst","extdata","NOBA_cod_files","NEAcod-2020","run","model.RData",
                            package = "atlantisom") 
#This is the SAM object
noba_fit <- noba_cod_out$fit

properties <- c("minAge","maxAge", "maxAgePlusGroup")

age_info <- lapply(properties, get, noba_fit$conf)
names(age_info) <- properties

#install SAM
remotes::install_github("fishfollower/SAM/stockassessment")
require(stockassessment)

#Month of survey/fishing
#survey_month <- 7
#fishing_month <- 1
